Multi-Core Model Checking and Maximum Satisfiability Applied to Hardware-Software Partitioning

### 2016-08-26 Docs/IJES/journal.tex
review Bounded Model Checking with ESBMC

Among the recent model checking techniques, there is one that combines model checking with satisﬁability solving. This technique, known as bounded model checking (BMC), does a very fast exploration of the state space, and for some types of problems, it offers large performance improvements over previous approaches, as \textcolor{blue}{presented by}~\cite{Biere2009}. In particular, BMC based on Boolean Satisfiability (SAT) has been introduced as a complementary technique to binary decision diagrams for alleviating the state explosion problem, as described by~\cite{Clarke2001}.

The basic idea of BMC is to check the negation of a given property at a given depth: given a transition system $M$, a property $\phi$, and a bound $k$, BMC unrolls the system $k$ times and translates it into a verification condition (VC) $\psi$  such that $\psi$ is satisfiable if and only if $\phi$ has a counterexample of depth $k$ or less, as defined in~\cite{Biere2009}. To cope with increasing software complexity, SMT solvers can be used as back-ends for solving the generated VCs, \textcolor{blue}{as presented by}~\cite{Cordeiro2012},~\cite{Armando2009},~\cite{Ganai2006}.

In this study, ESBMC has been used as a BMC tool to solve HW-SW partitioning problems, as mentioned in~\cite{Cordeiro2012}. 
In particular, there are two directives in ESBMC that can be used to guide it to solve an optimization problem: ASSUME and ASSERT. The directive ASSUME is responsible for ensuring the compliance of constraints (software costs), and the directive ASSERT controls the halt condition (minimum hardware cost). Then, with some C/C++ code, it is possible to guide ESBMC to solve optimization problems.

>>>>

Among recent model checking techniques, there is one that combines model checking with satisﬁability solving. This technique, known as bounded model checking (BMC), does a very fast exploration of the state space, and for specific types of problems, it offers large performance improvements over previous approaches, as \textcolor{blue}{presented by}~\cite{Biere2009}. In particular, BMC based on Boolean Satisfiability (SAT) has been introduced as a complementary technique to binary decision diagrams for alleviating the state-space explosion problem, as described by~\cite{Clarke2001}.

The basic idea of BMC is to check the negation of a given property at a given depth: given a transition system $M$, a property $\phi$, and a bound $k$, BMC unrolls the system $k$ times and translates it into a verification condition (VC) $\psi$  such that $\psi$ is satisfiable if and only if $\phi$ has a counterexample of depth $k$ or less, as defined in~\cite{Biere2009}. To cope with increasing software complexity, SMT solvers can be used as back-ends for solving the generated VCs, \textcolor{blue}{as presented by~\cite{Ganai2006},~\cite{Armando2009},~\cite{Cordeiro2012}}.

In this study, however, ESBMC has been used as a BMC tool to solve HW-SW partitioning problems, as mentioned in~\cite{Cordeiro2012}. 
In particular, there are two directives in ESBMC that can be used to guide it to solve an optimization problem: ASSUME and ASSERT. The directive ASSUME is responsible for ensuring the compliance of constraints (software costs), and the directive ASSERT controls the halt condition (minimum hardware cost). Then, with some C/C++ code, it is possible to guide ESBMC to solve optimization problems.
